Cryptographic techniques to ensure fair elections

### 2012-11-16 proposal/proposal.tex
Add email addresses
Rephrase abstract text

% title
\title{Cryptographic techniques to ensure fair elections}
\date{}
\author{Kelsey Francis, Curtis Free, Christopher Martin}

@@

	\begin{abstract}
		Traditional election processes are generally accepted by voters though they do not necessarily
		\emph{prove} to participants that the vote counting was fair. Researchers have developed
		mechanisms to replace or accompany these existing processes that \emph{do} provide such
		guarantees through use of cryptography, which allows some degree of ``fairness'' to be proven
		while keeping ballots secret. For this project, we will attempt to quantify what security goals
		must be met in order to consider an election ``fair,'' survey existing literature on the matter,
		and -- time permitting -- produce a proof-of-concept implementation of what we find to be the
		``best'' system or of our own that uses borrowed techniques in an attempt to meet all necessary
		goals.
	\end{abstract}

	\begin{multicols}{2}

>>>>

% title
\title{Cryptographic techniques to ensure fair elections}
\date{}
\author{
\begin{tabular}{c c c}
Kelsey Francis & Curtis Free & Christopher Martin \\
\small \tt{francis@gatech.edu} & \small \tt{curtis.free@gatech.edu} & \small \tt{chris.martin@gatech.edu}
\end{tabular}
}

@@

	\begin{abstract}
		Current election processes do not allow participants to verify the accuracy of vote counting.
		Applied cryptography research has yielded a number of candidate systems to replace or accompany
		voting existing voting procedures to provide fairness guarantees while maintaining ballot secrecy.
		We will define a set of security properties sufficient to make an election both ``fair'' and ``secret'',
		survey existing literature on the matter, and -- if time permits -- produce a proof-of-concept
		implementation of a system that meets these goals (either the best system we find, or one of
		our own creation using borrowed techniques).
	\end{abstract}
	\begin{multicols}{2}
